SPARQL on the Open, Decentralised Web

### 2016-06-22 dissertation/introdefhistory.tex

The problems are also discussed throughout
\cite{chalmers1999whatis}. It is interesting to consider the example
on page 25, where the author describes a method forwarded by Galileo
Galilei to measure the diameter of a star. The method was objective in
the sense if followed, it would yield the same value today as it did
when Galileo employed it. However, it relied on faulty assumptions and
is therefore invalid. The same kind of problem may occur in the
evaluation of e.g. SPARQL engines. If a benchmark relies on a faulty
workload, the application of the benchmark may seem objective to the
investigator, but its external validity should obviously be
challenged. Moreover, if the benchmark relied on a use case supplied
by e.g. an industrial partner, the validity could be further
challenged based on e.g. the restriction on viewpoint that this
represents. However, such challenges are scarcely seen in the literature.

@@

These challenges are inescapable, and therefore, it is important that
the researcher acknowledges such problems and explicitly details their
own personal motivations, visions and possible biases to let the
reader decide whether the researcher's subjective beliefs or other
external pressures has influenced the validity of their
contribution. It is also important to be humble and admit that even
though we as researchers treasure our objectivity, like Galileo, we
may not be in the ideal position to judge our own objectivity. We
should therefore detail our background to better equip the reader to
judge.

>>>>

The problems are also discussed throughout
\cite{chalmers1999whatis}. It is interesting to consider the example
on page 25, where the author describes a method forwarded by Galileo
Galilei to measure the diameter of a star. The method was objective in
the sense if followed, it would yield the same value today as it did
when Galileo employed it. However, it relied on faulty assumptions and
is therefore invalid. The same kind of problem may occur in the
evaluation of e.g. SPARQL engines. If a benchmark relies on a faulty
workload, the application of the benchmark may seem objective to the
investigator, but its external validity should obviously be
challenged. Moreover, if the benchmark relied on a use case supplied
by e.g. an industrial partner, the validity could be further
challenged based on e.g. the restriction on viewpoint that this
represents.

@@

These challenges are inescapable, and therefore, it is important that
the researcher acknowledges such problems and explicitly details their
own personal motivations, visions and possible biases to let the
reader decide whether the researcher's subjective beliefs or other
external pressures has influenced the validity of their
contribution. It is also important to be humble and admit that even
though we as researchers treasure our objectivity, like Galileo, we
may not be in the ideal position to judge our own objectivity, as
should be clear from the few challenges that research methods are
getting in the literature. We should therefore detail our background
to better equip the reader to judge.
